\textbf{AprilTrack: A Particle-Filter-based AprilTag Tracker}

### 2017-10-22 paper/paper.tex
Fixed typo
Fixed links, fixed figure numbering

\begin{figure*}[t]
	\centering
	\label{fig:error}
	\begin{tikzpicture}[trim axis left]
	\begin{axis}[
		width=\textwidth,
		height=9cm,
		title= {Average Corner Error on the Single-Tag Sequence},
		xlabel = {Time (Frame Number)},
		ylabel = {Average Corner Error (Pixels)},
		xmin=0, xmax=250,
		ymin=0, ymax=80,
		xtick={0,50,100,150,200,250},
		ytick={0,10,20,30,40,50,60, 70}
	]
	\addplot [
		color=blue,
		mark=none,
	] table {corner_error.dat};
\end{axis}
\end{tikzpicture}
	\caption{The average corner error between the hand-marked tag location and the tracked location. Much of the error comes from discrepancy between the tracker and the ground truth on the boundaries of the blurred tags. At around frames 30 and 200, the tracker loses the tag momentarily due to a sudden rotation but is able to recover without needing to be manually reset.}
\end{figure*}

@@

The AprilTrack algorithm was primarily evluated on a manually-labeled single-tag sequence with a moving tag. The algorithm was also run on an ego-motion multi-tag sequence which will be qualitatively discussed.
\footnote{Videos of the sequences and the tracker's performance are available online at https://www.youtube.com/watch?v=kV8z3st9rlk and https://www.youtube.com/watch?v=F5cFTLBlJ1s }

@@

When evaluated on the single-tag sequence, the algorithm ran with $N=3000$ at around $1$ fps on an i7 Haswell Intel CPU. In experiments with fewer particles, it was found that the algorithm could track a tag well with as few as $1000$ particles with around $5$ fps. With a more optimized C++ implementation, the framerate could perhaps be brought up to $10-15$ fps, making the algorithm (run with less agressive parameters) a possible candidate for real-time scenarios. Currently, the MATLAB implementation is intended for offline post-processing of a sequence and so real-time performance was not a focus of this research.

As shown in figure \ref{fig:error}, the pixel corner error is about 10 pixels for most of the sequence. The tracker loses the tag momentarily around frames 30 and 200 but is able to recover rapidly without any manual intervention. Much of the error observed throughout the sequence is the result of disagreement on the boundary of a blurred tag rather than a systematic issue with the tracker itself.

>>>>

\begin{figure*}[t]

	\centering
	\begin{tikzpicture}[trim axis left]
	\begin{axis}[
		width=\textwidth,
		height=9cm,
		title= {Average Corner Error on the Single-Tag Sequence},
		xlabel = {Time (Frame Number)},
		ylabel = {Average Corner Error (Pixels)},
		xmin=0, xmax=250,
		ymin=0, ymax=80,
		xtick={0,50,100,150,200,250},
		ytick={0,10,20,30,40,50,60, 70}
	]
	\addplot [
		color=blue,
		mark=none,
	] table {corner_error.dat};
\end{axis}
\end{tikzpicture}
	\label{fig:error}
	\caption{The average corner error between the hand-marked tag location and the tracked location. Much of the error comes from discrepancy between the tracker and the ground truth on the boundaries of the blurred tags. At around frames 30 and 200, the tracker loses the tag momentarily due to a sudden rotation but is able to recover without needing to be manually reset.}
\end{figure*}

@@

The AprilTrack algorithm was primarily evaluated on a manually-labeled single-tag sequence with a moving tag. The algorithm was also run on an ego-motion multi-tag sequence which will be qualitatively discussed.
\footnote{Videos of the sequence and the tracker's performance are available online at \url{https://www.youtube.com/watch?v=67LREs8fs9Q} and \url{https://www.youtube.com/watch?v=Rk87aE_9p-A}. The code is available online at \url{https://github.com/pfrommerd/tag-tracking-matlab}}

@@

When evaluated on the single-tag sequence, the algorithm ran with $N=3000$ at around $1$ fps on an i7 Haswell Intel CPU. In experiments with fewer particles, it was found that the algorithm could track a tag well with as few as $1000$ particles with around $5$ fps. With a more optimized C++ implementation, the framerate could perhaps be brought up to $10$ fps, making the algorithm (run with less agressive parameters) a possible candidate for real-time scenarios. Currently, the MATLAB implementation is intended for offline post-processing of a sequence and so real-time performance was not a focus of this research.

As shown in figure 4, the pixel corner error is about 10-20 pixels for most of the sequence. The tracker loses the tag momentarily around frame 30 but is able to recover rapidly without any manual intervention. Much of the error observed throughout the sequence is the result of disagreement on the boundary of a blurred tag rather than a systematic issue with the tracker itself.
